---
---

::: {.callout-tip}
## Learning Goals {.unnumbered}

By the end of this tutorial, you should be able to:

- Explain what **Quarto** is and why analysts use it
- Run R code inside a `.qmd` file and **render** a report
- Load a small dataset and compute a few **inventory KPIs**
- Produce a simple table and a basic plot
- Write a manager-friendly recommendation that separates **facts vs interpretation vs decision**
:::

## The Business Challenge

David Jones sells a wide range of seasonal products, including fashion items that see strong swings in demand around holidays like Christmas.

Inventory decisions are especially challenging for seasonal products because:

- Demand can spike unpredictably
- Promotions and discounts influence customer behaviour
- Regional preferences can differ
- Suppliers need advance notice to adjust deliveries

Right now, David Jones is using a fixed restocking rule:

> Every week, **100 units** are delivered to each region, no matter what.

But with the holiday season approaching, this rigid approach might not be enough.

**Management wants a one-page briefing outlining whether they should adapt their restocking rule.**

Your task is to review last year's data and advise David Jones on how to improve inventory decisions.

## Prepare these Exercises before Class 

Prepare these exercises before coming to class. Plan to spend 45 minutes on these exercises.

### Exercise 1: Approaches to Inventory Planning 

Read the article, "[A New Approach to Production and Inventory Planning](https://hbr.org/2023/09/a-new-approach-to-production-and-inventory-planning)," and answer the following questions in  2–3 sentences:

(a) Define the term "inventory management". What makes inventory management complicated for seasonal products?
(b) What is one key challenge businesses face in managing inventory today?
(c) How could this apply to a retailer like David Jones, especially during busy seasons like Christmas?

*Write your answer here*

### Exercise 2: A First Peek at Some Data

David Jones now wants to use **last year's data** to improve inventory decisions for the upcoming holiday season.

The data you have to work from are provided below:

| Week Commencing | Region    | Starting Inventory | Units Delivered | Units Sold | Ending Inventory | Price (AUD) | Promotion (Y/N) |
|-----------------|-----------|------------------|----------------|------------|-----------------|-------------|----------------|
| 25 Nov          | Sydney    | 500              | 100            | 100        | 500             | 50          | N              |
| 25 Nov          | Melbourne | 500              | 100            | 150        | 450             | 50          | N              |
| 2 Dec           | Sydney    | 500              | 100            | 180        | 420             | 45          | Y              |
| 2 Dec           | Melbourne | 450              | 100            | 220        | 330             | 45          | Y              |
| 9 Dec           | Sydney    | 420              | 100            | 150        | 370             | 45          | Y              |
| 9 Dec           | Melbourne | 330              | 100            | 100        | 330             | 45          | Y              |
| 16 Dec          | Sydney    | 370              | 100            | 400        | 70              | 40          | Y (Christmas)  |
| 16 Dec          | Melbourne | 330              | 100            | 400        | 30              | 40          | Y (Christmas)  |
| 23 Dec          | Sydney    | 70               | 100            | 120        | 50              | 50          | N              |
| 23 Dec          | Melbourne | 30               | 100            | 150        | -20 (backorder) | 50          | N              |

Before analysts run any code, they ask a simple question:

> **Can we trust this dataset enough to make a decision?**

Look at the David Jones data above and answer the questions below.

**(a)** Identify **5 potential issues** in the table. For each issue, classify it as:

* **1. Will break analysis/code**: formatting and/or type problems 
* **2. Unclear meaning**: we need a formal definition from the business
* **3. Decision risk**: could bias conclusions or lead to a bad recommendation

Fill in this template:

| Issue you noticed | Category (1/2/3) | Why it matters (1 sentence) |
| ----------------- | ---------------- | --------------------------- |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |

**(b)** Write one question you would email to the data owner today that would most improve your confidence in using the data to make a recommendation.

*Write your answer here*

### Exercise 3: Getting Set Up in Posit Cloud

Before we proceed, we need everyone working in the same environment. Complete the following steps:

**Step 1**: Log in to Posit Cloud

* Go to the Posit Cloud workspace link provided on the LMS.
* Log in using your University account.

**Step 2**: Make your own copy of the workshop project

- Locate the workshop project in Posit Cloud.
- Click Make a Copy to create your own version.

**Step 3**: Open the Quarto file

- In the Files pane, locate the workshop Quarto document: `tutorial_02_inventory.qmd`.
- Click it to open it in the editor.

**Step 4**: Render the document

* Find the Render button (top of the editor).
* Click Render.

If everything is set up correctly, a new tab should appear in your browser with the rendered content.

```{r}
# Write your answer here
```

### Exercise 4: R + Quarto Vocabulary Check (5 Quick Definitions)

Answer each in **one short sentence**.

**(a)** What does `<-` do in R?

**(b)** What is a **data frame** (and what does a row represent in our David Jones data)?

**(c)** What is a **function** in R? Give one example.

**(d)** What is a **code chunk** in a Quarto `.qmd` file?

**(e)** What does **Render** do in Quarto?

*Write your answer here*

### Exercise 5: Quick Recap of Preparation Work

With your group answer the following questions:

**(a)** In one sentence, what is the core trade-off in inventory management for a retailer like David Jones?

**(b)** What are the two biggest issues with the dataset presented in Exercise 2? Justify your choices.

*Write your answer here*

## In-Class Exercises

You will discuss these exercises in class with your peers in small groups and with your tutor. These exercises build from the exercises you have prepared above, you will get the most value from the class if you have completed those above before coming to class.

### Exercise 6: Loading and Inspecting Some Data

(a) Open the Posit Cloud Workspace for this workshop.

(b) Load the dataset by running this line of code:

```{r}
#| eval: false
library(readr)

inventory <- read_csv("data/inventory.csv") 
```

**(c)** We want to explain the code in (b) is doing, line by line.

* What does ` ```{r} ` mean in Quarto?
* What does `#| eval: false` do? 
* Do you need to change the `#| eval: false` setting to run the code when you render the file?
* What does `library(readr)` do?
* Explain what the assignment operator `<-`?, does.
* Is `read_csv()` a function or a variable?
* What does `"data/inventory.csv"` refer to?

(d)  Run each of the following commands, and explain the output to your group:

* `class(inventory)`
* `names(inventory)`
* `head(inventory)`
* `nrow(inventory)`
* `ncol(inventory)`

*Write your answer here*

### Exercise 7: First Steps Working with Data

Let's compute two manager-relevant variables:

1. **Revenue by region**, and
2. **Inventory risk** (how low inventory gets).

::: {.callout-tip}

You will need to use the following R commands in this exercise:

* column access with `$`
* logical filtering with `==`
* multiplication with (`*`)
* `sum()` and `min()`

:::

**(a)** Create a new column called `revenue` that equals `units_sold` times  `unit_price`.

```{r}
#| eval: false

# Create revenue using simple arithmetic
inventory$revenue <- YOUR_CODE_HERE
```

**(b)** Compute total revenue for both Sydney and Melbourne

```{r}
#| eval: false

# first filter the relevant rows of data
syd <-  inventory$revenue[YOUR_CONDITION]  # Condition should be about region == Sydney 
mel <-  YOUR_CODE_HERE[YOUR_CONDITION]     # Condition should be about region == Melbourne 

# Then compute total revenue
rev_syd  <- sum( YOUR_CODE_HERE )
rev_melb <- YOUR_CODE_HERE

rev_syd
rev_melb
```

**(c)** Compute total units sold for Sydney and Melbourne. 

::: {.callout-warning}

Use the code from (b) as a template for this exercise. The steps you need to perform are very similar.

:::

```{r}
#| eval: false

YOUR_CODE_HERE

sold_syd  <- sum( YOUR_CODE_HERE )
sold_melb <- YOUR_CODE_HERE

sold_syd
sold_melb
```

**(d)** Find the minimum ending inventory for each region

```{r}
#| eval: false

min_end_syd  <- YOUR_CODE_HERE
min_end_melb <- YOUR_CODE_HERE

min_end_syd
min_end_melb
```

**(e)** A backorder occurs when `ending_inventory` is negative.

1. Does *any* row have `ending_inventory < 0`?
2. If yes, display those rows.

```{r}
#| eval: false

any_backorders <- any(YOUR_CODE_HERE)  # Should use the ending_inventory column
                                       # to check whether < 0 
any_backorders

backorder_rows <- inventory[ YOUR_CODE_HERE , ]  # Use the same condition as above
backorder_rows
```

```{r}
# Write your answer here
```

### Exercise 8: Turning Numbers into a Story (Before We Recommend Anything)

You've just computed a few KPIs in R (revenue, units sold, minimum ending inventory, and whether backorders occurred).

Before we jump to "what should David Jones order?", we need to answer a more basic question:

> **What do the numbers actually tell us — and what do they *not* tell us?**

**(a)** What are the **two most important facts** you learned from your KPIs?  

Write them as two short bullet points (each should reference a KPI you computed).

**(b)** Based on those facts, what is your group's best guess about what will happen next week if David Jones keeps doing the same thing?

**(c)** What is one caveat you would tell management about your answer to (b)?

*Write your answer here*

### Exercise 8: Planning for This Year's Holiday Season

David Jones’ supplier is asking you to confirm delivery quantities **now**, so they can prepare for the season ahead.

(a) How many units should you order for Sydney and Melbourne for the first week of the holiday season?
(b) Justify your decision based on last year's patterns and your reasoning. Consider factors like demand trends, regional differences, price effects, and promotion timing.
(c) Suppose the supplier has limited capacity and can only supply 200 units total for the first week.  How would you allocate this stock between Sydney and Melbourne? What are the risks of your choice?

*Write your answer here*

