---
---

::: {.callout-tip}
## Learning Goals {.unnumbered}

By the end of this tutorial, you should be able to:

- Explain what **Quarto** is and why analysts use it
- Run R code inside a `.qmd` file and **render** a report
- Load a small dataset and compute a few **inventory KPIs**
- Produce a simple table and a basic plot
- Write a manager-friendly recommendation that separates **facts vs interpretation vs decision**
:::

## The Business Challenge

David Jones sells a wide range of seasonal products, including fashion items that see strong swings in demand around holidays like Christmas.

Inventory decisions are especially challenging for seasonal products because:

- Demand can spike unpredictably
- Promotions and discounts influence customer behaviour
- Regional preferences can differ
- Suppliers need advance notice to adjust deliveries

Right now, David Jones is using a fixed restocking rule:

> Every week, **100 units** are delivered to each region, no matter what.

But with the holiday season approaching, this rigid approach might not be enough.

**Management wants a one-page briefing outlining whether they should adapt their restocking rule.**

Your task is to review last year's data and advise David Jones on how to improve inventory decisions.

## Prepare these Exercises before Class 

Prepare these exercises before coming to class. Plan to spend 45 minutes on these exercises.

### Exercise 1: Approaches to Inventory Planning 

Read the article, "[A New Approach to Production and Inventory Planning](https://hbr.org/2023/09/a-new-approach-to-production-and-inventory-planning)," and answer the following questions in  2–3 sentences:

(a) Define the term "inventory management". What makes inventory management complicated for seasonal products?
(b) What is one key challenge businesses face in managing inventory today?
(c) How could this apply to a retailer like David Jones, especially during busy seasons like Christmas?

*Write your answer here*

### Exercise 2: A First Peek at Some Data

David Jones now wants to use **last year's data** to improve inventory decisions for the upcoming holiday season.

The data you have to work from are provided below:

| Week Commencing | Region    | Starting Inventory | Units Delivered | Units Sold | Ending Inventory | Price (AUD) | Promotion (Y/N) |
|-----------------|-----------|------------------|----------------|------------|-----------------|-------------|----------------|
| 25 Nov          | Sydney    | 500              | 100            | 100        | 500             | 50          | N              |
| 25 Nov          | Melbourne | 500              | 100            | 150        | 450             | 50          | N              |
| 2 Dec           | Sydney    | 500              | 100            | 180        | 420             | 45          | Y              |
| 2 Dec           | Melbourne | 450              | 100            | 220        | 330             | 45          | Y              |
| 9 Dec           | Sydney    | 420              | 100            | 150        | 370             | 45          | Y              |
| 9 Dec           | Melbourne | 330              | 100            | 100        | 330             | 45          | Y              |
| 16 Dec          | Sydney    | 370              | 100            | 400        | 70              | 40          | Y (Christmas)  |
| 16 Dec          | Melbourne | 330              | 100            | 400        | 30              | 40          | Y (Christmas)  |
| 23 Dec          | Sydney    | 70               | 100            | 120        | 50              | 50          | N              |
| 23 Dec          | Melbourne | 30               | 100            | 150        | -20 (backorder) | 50          | N              |

Before analysts run any code, they ask a simple question:

> **Can we trust this dataset enough to make a decision?**

Look at the David Jones data above and answer the questions below.

**(a)** Identify **5 potential issues** in the table. For each issue, classify it as:

* **1. Will break analysis/code**: formatting and/or type problems 
* **2. Unclear meaning**: we need a formal definition from the business
* **3. Decision risk**: could bias conclusions or lead to a bad recommendation

Fill in this template:

| Issue you noticed | Category (1/2/3) | Why it matters (1 sentence) |
| ----------------- | ---------------- | --------------------------- |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |
|                   |                  |                             |

**(b)** Write one question you would email to the data owner today that would most improve your confidence in using the data to make a recommendation.

*Write your answer here*

### Exercise 3: Getting Set Up in Posit Cloud

Before we proceed, we need everyone working in the same environment. Complete the following steps:

**Step 1**: Log in to Posit Cloud

* Go to the Posit Cloud workspace link provided on the LMS.
* Log in using your University account.

**Step 2**: Make your own copy of the workshop project

- Locate the workshop project in Posit Cloud.
- Click Make a Copy to create your own version.

**Step 3**: Open the Quarto file

- In the Files pane, locate the workshop Quarto document: `tutorial_02_inventory.qmd`.
- Click it to open it in the editor.

**Step 4**: Render the document

* Find the Render button (top of the editor).
* Click Render.

If everything is set up correctly, a new tab should appear in your browser with the rendered content.

```{r}
# Write your answer here
```

### Exercise 4: R + Quarto Vocabulary Check (5 Quick Definitions)

Answer each in **one short sentence**.

**(a)** What does `<-` do in R?

**(b)** What is a **data frame** (and what does a row represent in our David Jones data)?

**(c)** What is a **function** in R? Give one example.

**(d)** What is a **code chunk** in a Quarto `.qmd` file?

**(e)** What does **Render** do in Quarto?

*Write your answer here*

### Exercise 5: Title

This is the text for the question, with its accompanying code 

```{r}
# Example code for the question
1 + 1
```

```{r}
# Write your answer here
```

## In-Class Exercises

You will discuss these exercises in class with your peers in small groups and with your tutor. These exercises build from the exercises you have prepared above, you will get the most value from the class if you have completed those above before coming to class.

### Exercise 1: Title

This is the text for the question, with its accompanying code 

```{r}
# Example code for the question
1 + 1
```

```{r}
# Write your answer here
```

### Exercise 7: Title

This is the text for the question, with its accompanying code 

```{r}
# Example code for the question
1 + 1
```

```{r}
# Write your answer here
```

### Exercise 8: Title

This is the text for the question, with its accompanying code 

```{r}
# Example code for the question
1 + 1
```

```{r}
# Write your answer here
```

### Exercise 9: Title

This is the text for the question, with its accompanying code 

```{r}
# Example code for the question
1 + 1
```

```{r}
# Write your answer here
```

### Exercise 10: Title

This is the text for the question, with its accompanying code 

```{r}
# Example code for the question
1 + 1
```

```{r}
# Write your answer here
```

