## Key R functions used in this notebook

This page collects every new R function you used in this tutorial, in one place, as a quick-reference glossary. Each function below follows the same format:

- **Package:** where the function comes from. Most functions you'll meet early on are **Base R** (built into R, no setup needed). Others live in packages that must be loaded first with `library()`.
- **What it does:** a plain-English explanation, no jargon.
- **Why you'd use it:** the everyday analyst reason you'd reach for it.
- **Arguments:** the inputs you put inside the parentheses `()` to tell the function exactly what to work on. Some are required, some are optional. Arguments listed here are not necessarily exhaustive.
- **Example:** the function used on this week's `inventory` dataset.

For more information on any function, use ?`function_name` in the R console (e.g. `?read_csv`) to see the official documentation, which includes a full list of arguments, descriptions, and often many examples.

### `library()`

**Package:** Base R

**What it does:** Loads an R package, a bundle of extra functions someone else has built, into your current session so you can use them.

**Why you'd use it:** R comes with a lot built in, but most real analysis relies on add-on packages too. You need to load and run a package with `library()` to use that package's functions.

**Arguments:**

- `package` — the name of the package you want to load. Written without quotation marks (e.g. `readr`, not `"readr"`).

**Example:**

```{r}
#| eval: false
# Load the readr package so its functions (like read_csv()) become available
library(readr)
```

### `read_csv()`

**Package:** readr

**What it does:** Reads a CSV file and stores it in R as a data frame.

**Why you'd use it:** Getting your data into R is almost always the first step of any analysis.

**Arguments:**

- `file` — the file path, in quotation marks, telling R where to find the CSV file, starting from your working directory / root folder (e.g. `"data/inventory.csv"`).

**Example:**

```{r}
#| eval: false
# Import the weekly inventory data into an object called "inventory"
inventory <- read_csv("data/inventory.csv")
```

### `class()`

**Package:** Base R

**What it does:** Tells you what *type* of object something is (e.g. a data frame, a number, or text).

**Why you'd use it:** It's a quick sanity check right after importing data, to confirm R read it in the way you expected.

**Arguments:**

- `x` — the R object you want to check (e.g. a data frame, a column, a single value).

**Example:**

```{r}
#| eval: false
class(inventory)
```

### `names()`

**Package:** Base R

**What it does:** Lists the column (variable) names of a data frame.

**Why you'd use it:** To see all the variables in a dataset or remind yourself of precise column names when writing code.

**Arguments:**

- `x` — the data frame (or other object) whose names you want to list.

**Example:**

```{r}
#| eval: false
names(inventory)
```

### `head()`

**Package:** Base R

**What it does:** Shows just the first few rows of a data frame (6 rows, by default).

**Why you'd use it:** To preview your data without flooding the screen, handy for datasets with hundreds or thousands of rows.

**Arguments:**

- `x` — the data frame you want to preview.
- `n` — *(optional)* how many rows to show. Defaults to 6 if you don't specify one (e.g. `head(inventory, 10)` shows 10 rows).

**Example:**

```{r}
#| eval: false
head(inventory)
```

### `nrow()`

**Package:** Base R

**What it does:** Counts how many rows a data frame has.

**Why you'd use it:** To know how many observations you're working with, for example, how many weeks of data you have.

**Arguments:**

- `x` — the data frame you want to count the rows of.

**Example:**

```{r}
#| eval: false
nrow(inventory)
```

### `ncol()`

**Package:** Base R

**What it does:** Counts how many columns a data frame has.

**Why you'd use it:** To know how many variables each row records.

**Arguments:**

- `x` — the data frame you want to count the columns of.

**Example:**

```{r}
#| eval: false
ncol(inventory)
```

### `any()`

**Package:** Base R

**What it does:** Checks a condition across a whole column of values and returns a single `TRUE` if at least one value meets it, or `FALSE` if none do.

**Why you'd use it:** To quickly ask "does X occur anywhere in my data?", for example, checking whether any backorders occurred.

**Arguments:**

- `...` — one or more logical conditions (statements that are either `TRUE` or `FALSE`), such as `inventory$ending_inventory < 0`.

**Example:**

```{r}
#| eval: false
# Is there at least one row where ending inventory is negative?
any(inventory$ending_inventory < 0)
```

### `sum()`

**Package:** Base R

**What it does:** Adds up every value in a numeric column to give a single total.

**Why you'd use it:** To calculate totals, like total units sold or total revenue, from many rows of data.

**Arguments:**

- `...` — one or more numeric values or columns to add together, such as `inventory$units_sold`.

**Example:**

```{r}
#| eval: false
# Total number of units sold across all rows
sum(inventory$units_sold)
```
