<!-- question-type: inclass -->
### Exercise 7: First Steps Working with Data

Let's compute two manager-relevant variables:

1. **Revenue by region**, and
2. **Inventory risk** (how low inventory gets).


::: {.callout-tip}

We will use the following R commands in this exercise:

* column access with `$`
* logical filtering with `==`
* multiplication with (`*`)
* Summing rows of data with `sum()`
* Finding matches with `any()`

:::

**(a)** Create a new column called `revenue` that equals `units_sold` times  `unit_price` by running the code below. Explain what the code is doing.

```{r}
#| eval: false

# Create revenue using simple arithmetic
inventory$revenue <- inventory$units_sold * inventory$unit_price
```

**(b)** Run the code below to compute total revenue for both Sydney and Melbourne. Explain what step 1, step 2 and step 3 are doing.

```{r}
#| eval: false

# STEP 1: EXPLAIN WHAT IS HAPPENING
syd_data <- inventory[inventory$region == "Sydney", ]
mel_data <- inventory[inventory$region == "Melbourne", ]

# STEP 2: EXPLAIN WHAT IS HAPPENING
rev_syd  <- sum(syd_data$revenue)
rev_melb <- sum(mel_data$revenue)

# STEP 3: EXPLAIN WHAT IS HAPPENING
rev_syd
rev_melb
```

**(c)** A backorder occurs when `ending_inventory` is negative.

1. Does *any* row have `ending_inventory < 0`?
2. If yes, display those rows.

Run the code below and explain the steps.

```{r}
#| eval: false

# STEP 1: EXPLAIN WHAT IS HAPPENING 
any_backorders <- any(inventory$ending_inventory < 0)

# STEP 2: EXPLAIN WHAT IS HAPPENING 
any_backorders

# STEP 3: EXPLAIN WHAT IS HAPPENING 
backorder_rows <- inventory[inventory$ending_inventory < 0, ]

# STEP 4: EXPLAIN WHAT IS HAPPENING 
backorder_rows
```



<!-- BEGIN PROFILE:r-teaching-guide -->
::: {.content-visible when-profile="r-teaching-guide"}

::: {.teaching-block}

::: {.teaching-block-header}
Teaching Note
:::

::: {.teaching-block-body}

🎯 **Learning Objective** 
Students should:

- **Compute** a new variable using simple arithmetic (`revenue = units_sold * unit_price`).  
- **Subset** rows using a logical condition (`region == "Sydney"` / `"Melbourne"`).  
- **Summarise** data with `sum()` to produce manager-relevant KPIs.  
- **Diagnose** common beginner errors (wrong column names, wrong filter, forgetting to evaluate chunks).

✅   **Core Concepts to Highlight**

- **New variable (column):** `inventory$revenue <- ...` adds a column to the data frame.  
- **Logical filtering:** `inventory$region == "Sydney"` returns TRUE/FALSE for each row; using it inside `[...]` keeps only matching rows.  
- **`sum()`:** reduce a vector to a single number (total).  
- **Sanity check habit:** after each step, print objects to confirm they look plausible.



💬 **Suggested In-Class Prompts** (if needed)

- “What does `inventory$revenue <- ...` change about the dataset?”  
- “What type of thing is `inventory$region == "Sydney"`? What does it look like?”  
- “Why do we create `syd_data` first instead of putting everything inside `sum()`?”  
- “Which KPI is about *size/value* (revenue) and which is about *risk* (ending inventory)?”  
- “If you got `NA`, what’s the first thing you would check?”

📌 **Common Misunderstandings**

- **Column name mismatch** (`units_sold` vs `Units Sold`, etc.).  
  - Fix: run `names(inventory)` and copy-paste the exact name.  
- **Filtering mistake** (`inventory$region = "Sydney"` or missing `==`).  
  - Fix: remind: `==` compares, `<-` assigns.  
- **Forgetting quotes** (`region == Sydney`).  
  - Fix: text values need quotes: `"Sydney"`.  
- **Using the whole column in `sum()` without filtering** (they compute total across both regions).  
  - Fix: ask them to print `syd_rev` and check it’s shorter than full dataset.  
- **Chunk not running** because `#| eval: false` is still present.  
  - Fix: remove/flip to true; rerender; confirm objects appear in Environment.  
- **`min()` returns weird values** because `ending_inventory` imported as text.  
  - Fix: link back to data-quality triage; ensure the clean CSV is being used.

:::

:::

:::
<!-- END PROFILE:r-teaching-guide -->

<!-- BEGIN PROFILE:r-solutions -->
::: {.content-visible when-profile="r-solutions" when-profile="r-teaching-guide"}

::: {.solution-block}

::: {.solution-block-header}
Solution
:::

::: {.solution-block-body}


**(a)** Create `revenue = units_sold * unit_price`

```{r}
#| eval: false

inventory$revenue <- inventory$units_sold * inventory$unit_price
```

Explanation: Creates a new column called `revenue` in the inventory dataset by multiplying two existing columns of data together.


**(b)** Total revenue for Sydney and Melbourne

```{r}
#| eval: false

# STEP 1: Create two separate datasets by filtering the rows of inventory by region.
# The expression inside the square brackets tells R which rows to keep.
# - inventory$region == "Sydney" keeps only rows for Sydney
# - inventory$region == "Melbourne" keeps only rows for Melbourne
# The comma before ] means: keep all columns for those rows.
syd_data <- inventory[inventory$region == "Sydney", ]
mel_data <- inventory[inventory$region == "Melbourne", ]

# STEP 2: Take the revenue column from each regional dataset and add up all values.
# This gives total revenue for Sydney and total revenue for Melbourne.
rev_syd  <- sum(syd_data$revenue)
rev_melb <- sum(syd_data$revenue)

# STEP 3: Print the two totals to the screen.
# This lets us compare total revenue across the two regions.
rev_syd
rev_melb
```




**(c)** Backorders (ending inventory < 0)

```{r}
#| eval: false

# STEP 1: Create a single TRUE/FALSE value that checks whether
# any product in the inventory data has negative ending inventory.
# If at least one row has ending_inventory < 0, this will be TRUE.
any_backorders <- any(inventory$ending_inventory < 0)

# STEP 2: Display the value stored in any_backorders.
# This tells us whether any backorders exist at all. 
any_backorders

# STEP 3: Create a new dataset containing only the rows where
# ending_inventory is negative. These are the cases where backorders occurred.
backorder_rows <- inventory[inventory$ending_inventory < 0, ]

# STEP 4: Display the filtered dataset of backorder rows.
# This lets us inspect which products/regions/periods had backorders.
backorder_rows
```

:::

:::

:::
<!-- END PROFILE:r-solutions -->